---
title: "Developing_Data_Products_w1"
author: "Naruhiko"
date: "02/02/2020"
output: html_document
header-includes:
  \usepackage[sfdefault, light]{roboto}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment week 2
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

```{r, echo = FALSE}
library(leaflet)
suppressPackageStartupMessages(library(tidyverse))
my_map <- leaflet() %>%
  addTiles()
```

## Including markers
Highighting the engineering school I studied during graduation.

```{r pressure, echo=FALSE}
my_map <- my_map %>% 
  addMarkers(lat = -19.869629, lng = -43.963236,
             popup = "Escola de Engenharia UFMG")
my_map
```


## Adding other markers
Now some more markers from another university from my state.

```{r, echo = FALSE}
library(openxlsx)
library(RColorBrewer)
puc_icon <- makeIcon(
  iconUrl = 'https://seminarioguimaraesrosa.files.wordpress.com/2016/06/brasao-puc-minas.jpg',
  iconWidth = 31*640/548, iconHeight = 31,
  iconAnchorX = 31*640/548/2, iconAnchorY = 31/2
)
puc_minas <- read.xlsx('Dados Puc - 2018.xlsx')
puc_locations <- puc_minas %>%
  select(Lat, Lng) %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(# clusterOptions = markerClusterOptions(),
             weight = 3,
             opacity = 1000,
             radius = (puc_minas$Total)/10,
             color = brewer.pal(n = nrow(puc_minas), name = 'Paired')) %>%
  addLegend(labels = puc_minas$Unidade, colors = brewer.pal(nrow(puc_minas), 'Paired'))
puc_locations

```

